Online supplement accompanying `The Locally Gaussian Partial Correlation'

### 2021-01-26 responses2/responses.Rmd
Few corrections to the responses, added empty transfer documents

\textbf{Our response:} Thank you, we have updated the notation according to your comment. The expression below eq. (10) follows directly from the definition of conditional independence in terms of density functions. Two variables are conditionally independent given a third variable if and only if their corresponding \textit{joint} conditional density given the third variable is equal to the product of their corresponding \textit{marginal} conditional densities given the third variable. We have made this clear by adding "\textit{by definition}" just before the expression.

>>>>

\textbf{Our response:} Thank you, we have updated the notation according to your comment. The expression below eq. (10) contained an error under each of the square root signs which has been corrected.
